# Paper Rank
## Read Data

Read data and transfer the class of it's date column from factor to date
```{r readdata, cache=TRUE}
paperrank <- read.table("activity 2.csv", quote = "",sep = ",", header = TRUE)
paperrank <- transform(paperrank, X.date. = as.Date(as.character(X.date.),
                                                    format = "\"%Y-%m-%d\""))
summary(paperrank)
```

## First Question: what is mean total number of steps taken per day?

Calculate the total steps each day
```{r totalstep}
library(dplyr)
library(ggplot2)
paperrank <- tbl_df(paperrank)
totalstep <- paperrank %>%
        filter(!is.na(X.steps.)) %>%
        group_by(X.date.) %>%
        summarize( totalstep = sum(X.steps.))
totalstep
```

Draw the histogram of total steps
```{r hist, cache=TRUE}
g <- ggplot(totalstep,aes(totalstep))
g + geom_histogram()
```

Calculate the mean step
```{r mean, cache=TRUE}
meanstep <- as.numeric(summarize(totalstep, mean = mean(totalstep)))
meanstep
```

Calculate the median step
```{r median, cache=TRUE}
medianstep <- as.numeric(summarize(totalstep, medain = median(totalstep)))
medianstep
```

## Second question: What is the average daily activity pattern?

Make a time series plot of the 5-minute interval and the average number of steps taken, averaged across all days
```{r averagedaily activity}
paperrank <- tbl_df(paperrank)
step <- paperrank %>%
        mutate(hours = as.integer(X.interval./100),
               minutes = as.integer(X.interval.%%100)) %>%
        mutate(hm=paste(hours, minutes, "00",sep=":")) %>%
        mutate(times = paste(X.date., hm, sep=" ")) %>%
        select(X.steps., times) %>%
        transform(dates = as.POSIXlt(times)) %>%
        select(X.steps.,dates)
names(step) <- c("steps","dates")
g <- ggplot(step, aes(dates,steps))
g + geom_line()
```


## Third question: Imputing missing values

Calculate and report the total number ofrows with missing value
```{r missing value}
sum(is.na(paperrank))
```

Strategy of filling missing values: the NA value equal to the mean for that 5-minute interval

New dataset with missing data filled in:
```{r newdataset}
library(dplyr)
library(ggplot2)
paperrank <- tbl_df(paperrank)
intervalmeanstep <- paperrank %>%
        filter(!is.na(X.steps.)) %>%
        group_by(X.interval.) %>%
        summarize( meanstep = mean(X.steps.))
paperrank2 <- paperrank
paperrank3 <- paperrank2 %>%
        filter(is.na(paperrank2$X.steps.))
paperrank3 <- merge(paperrank3, intervalmeanstep, by = "X.interval.")
paperrank3 <- paperrank3 %>% 
        mutate(X.steps. = ceiling(meanstep)) %>%
        select(X.steps.,X.date.,X.interval.)

paperrank2 <- rbind(paperrank2[!is.na(paperrank2$X.steps.),],paperrank3)
paperrank2 <- paperrank2 %>% 
        arrange(X.date.)
summary(paperrank2)
```

Plot histogram of the total number of steps taken each day:
```{r hist2}
totalstep2 <- paperrank2 %>%
        group_by(X.date.) %>%
        summarize( totalstep = sum(X.steps.))
g <- ggplot(totalstep2,aes(totalstep))
g + geom_histogram()
```

Mean value of this:
```{r mean2}
as.numeric(summarize(totalstep2, mean = mean(totalstep)))
```

Median value of this:
```{r median2}
as.numeric(summarize(totalstep2, medain = median(totalstep)))
```

Because the missing data is filled by 5-minute intervals, so the mid part of the histogram increased rapidly. On the other hand, mean and median value changed little.

## Forth question: Are there differences in activity patterns between weekdays and weekends?

divide data set by using two levels: weekday and weekend
```{r divide}
library(dplyr)
paperrank2 <- tbl_df(paperrank2)
step2 <- paperrank2 %>%
        mutate(hours = as.integer(X.interval./100),
              minutes = as.integer(X.interval.%%100)) %>%
        mutate(hm=paste(hours, minutes, "00",sep=":")) %>%
        mutate(times = paste(X.date., hm, sep=" ")) %>%
        select(X.steps., times) %>%
        transform(dates = as.POSIXlt(times)) %>%
        select(X.steps.,dates) %>%
        rename(steps = X.steps.)
step2 <- mutate(step2, weekday = weekdays(step2$dates))
step2[step2$weekday %in% 
              c("星期一","星期二","星期三","星期四","星期五"),]$weekday <- "weekday"
step2[step2$weekday %in% c("星期六","星期日"),]$weekday <- "weekend"
summary(step2)
```

draw the picture
```{r drawpicture}
g <- ggplot(step2, aes(dates,steps))
g + geom_line() + facet_grid(weekday~.)
```







